### 2016-12-13 poster/poster.tex
poster tweaks and images added (2)

%% BOX 0
\headerbox{Hardware}{name=hardware,column=1,row=0.00,span=1}{
\vspace{0.5em}
\hspace{-15pt}
\begin{tabular}{cc}
\parbox{0.85\textwidth}{
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{CPU}: Intel Core i7-5930K, 6 core, 12 thread (3.5 GHz)
\item \textbf{Memory}: G.SKILL Ripjaws 4 Series (8 x 8 GB)
\item \textbf{GPU}: GeForce GTX TITAN X (2 x 12 GB)
\end{itemize}\vspace*{35pt}
} & \hspace*{-10pt}
\includegraphics[scale=.1]{graphics/titanx.png}\vspace*{-35pt}
\end{tabular}
% TODO: maybe convert into methodology section -- what experiments we ran (until convergence, single epoch, single batch)
}
\headerbox{Benchmarking strategy}{name=methods,column=1,row=0.1965, span=1}{
\vspace{5pt}
\begin{itemize}
\item \textbf{Timing}:\\convergence, single epoch, single batch
\item \textbf{GPU Profiling}:\\overall, matrix multiply, specific GPU metrics
\end{itemize}
\vspace{5pt}
}

>>>>

%% BOX 0
\headerbox{Hardware}{name=hardware,column=1,row=0.00,span=1}{
\vspace{0.5em}
\hspace{-15pt}
\begin{tabular}{cc}
\parbox{0.85\textwidth}{
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{CPU}: Intel Core i7-5930K, 6 core, 12 thread (3.5 GHz)
\item \textbf{Memory}: G.SKILL Ripjaws 4 Series (8 x 8 GB)
\item \textbf{GPU}: GeForce GTX TITAN X (2 x 12 GB)
\end{itemize}\vspace*{35pt}
} & \hspace*{-10pt}
\includegraphics[scale=.1]{graphics/titanx.png}\vspace*{-35pt}
\end{tabular}
% TODO: maybe convert into methodology section -- what experiments we ran (until convergence, single epoch, single batch)
}
\headerbox{Benchmarking strategy}{name=methods,column=1,row=0.1965, span=1}{
\vspace{5pt}
\begin{itemize}
\item \textbf{Timing}: \textit{how long does it take to train/test?}\\ till convergence, single epoch, single batch
\item \textbf{GPU Profiling}: \textit{using the CUDA Profiler}\\overall, matrix multiply, specific GPU metrics
\end{itemize}
\vspace{5pt}
}
